A 2-Norm Condition Number for B\'{e}zier Curve Intersection

### 2019-06-17 doc/paper.tex
Added "trivial" example showing equivalence to 1D case.

In \cite[Chapter~25, Section 25.4]{Higham2002} a similar definition is
given. Instead of bounding the perturbations component-wise, it bounds
the entire perturbation vector \(\bm{\delta}\)
\begin{equation}
  \lim_{\eps \to 0} \left(\sup_{\left \lVert \bm{\delta} \right \rVert \leq
  \eps \left \lVert \bm{c} \right \rVert} \frac{\left \lVert
  J^{-1}\left(\bm{\alpha}\right) \sum_j \delta_j
  \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
  \left \lVert \bm{\alpha} \right \rVert}\right).
\end{equation}
It's possible to rewrite \(\sum_j \delta_j \phi_j\left(\bm{\alpha}\right) =
F_{\bm{c}} \bm{\delta}\) where \(F_{\bm{c}} =
\left[\frac{\partial F_i}{\partial c_j}\right]_{ij} =
\left[\begin{array}{c c c} \phi_0\left(\bm{\alpha}\right) & \cdots &
\phi_n\left(\bm{\alpha}\right) \end{array}\right]\) is the Jacobian of \(F\)
with respect to the coefficients \(\bm{c}\). With this representation, the
Higham condition number has a closed form since
\begin{equation}
  \left \lVert
  J^{-1} F_{\bm{c}} \bm{\delta} \right \rVert / \eps \leq
  \left \lVert J^{-1} F_{\bm{c}} \right \rVert \left \lVert \bm{\delta} \right
  \rVert / \eps \leq \left \lVert J^{-1} F_{\bm{c}} \right \rVert \left \lVert
  \bm{c} \right \rVert
\end{equation}
for any matrix norm that is compatible with the vector norm used on
\(\bm{\delta}\). The Frobenius matrix norm and Euclidean vector norm can be
combined to give a condition number that is straightforward to compute:
\begin{equation}
  \kappa_H = \left \lVert J^{-1} F_{\bm{c}} \right \rVert_F
  \frac{\left \lVert \bm{c}
  \right \rVert_2}{\left \lVert \bm{\alpha} \right \rVert_2}.
\end{equation}

@@

>>>>

In \cite[Chapter~25, Section 25.4]{Higham2002} a similar definition is
given. Instead of bounding the perturbations component-wise, it bounds
the entire perturbation vector \(\bm{\delta}\)
\begin{equation}
  \lim_{\eps \to 0} \left(\sup_{\left \lVert \bm{\delta} \right \rVert \leq
  \eps \left \lVert \bm{c} \right \rVert} \frac{\left \lVert
  J^{-1}\left(\bm{\alpha}\right) \sum_j \delta_j
  \phi_j\left(\bm{\alpha}\right) \right \rVert / \eps}{
  \left \lVert \bm{\alpha} \right \rVert}\right).
\end{equation}
It's possible to rewrite \(\sum_j \delta_j \phi_j\left(\bm{\alpha}\right) =
F_{\bm{c}} \bm{\delta}\) where \(F_{\bm{c}} =
\left[\frac{\partial F_i}{\partial c_j}\right]_{ij} =
\left[\begin{array}{c c c} \phi_0\left(\bm{\alpha}\right) & \cdots &
\phi_n\left(\bm{\alpha}\right) \end{array}\right]\) is the Jacobian of \(F\)
with respect to the coefficients \(\bm{c}\). With this representation, the
Higham condition number has a closed form since
\begin{equation}
  \left \lVert
  J^{-1} F_{\bm{c}} \bm{\delta} \right \rVert / \eps \leq
  \left \lVert J^{-1} F_{\bm{c}} \right \rVert \left \lVert \bm{\delta} \right
  \rVert / \eps \leq \left \lVert J^{-1} F_{\bm{c}} \right \rVert \left \lVert
  \bm{c} \right \rVert
\end{equation}
for any matrix norm that is compatible with the vector norm used on
\(\bm{\delta}\). The Frobenius matrix norm and Euclidean vector norm can be
combined to give a condition number that is straightforward to compute:
\begin{equation}\label{eq:higham-cond-num}
  \kappa_H = \left \lVert J^{-1} F_{\bm{c}} \right \rVert_F
  \frac{\left \lVert \bm{c}
  \right \rVert_2}{\left \lVert \bm{\alpha} \right \rVert_2}.
\end{equation}

@@

\subsection{Collapsing to One-dimensional Case}

One key argument for choosing Definition~\ref{defn:abstract-cond-num} over
the Highham condition number \(\kappa_H\) from~\eqref{eq:higham-cond-num} is
that \(\kappa_{\bm{\alpha}}\) is a natural extension of the condition number
for the equivalent one-dimensional problem. To see that this is so, we'll
define a "trivial" example by starting with a polynomial \(p(s)\) in Bernstein
form and a simple root \(\alpha\).

We define the B\'{e}zier curves \(b_0(s) = \left[ \begin{array}{c} p(s) \\ 0
\end{array}\right]\) and \(b_1(t) = \left[ \begin{array}{c} 0 \\ t
\end{array}\right]\). These curves intersect when \(\beta = 0\) and
\(\alpha\) is a root of \(p(s)\).
At such an intersection \(\mu_1 = \widetilde{p}(\alpha) + 0\),
\(\mu_2 = 0 + \beta = 0\) and
\begin{equation}
J^{-1} = \left[ \begin{array}{c c} 1 / p'(\alpha) & 0 \\ 0 & -1 \end{array}\right]
\end{equation}
so that \(\bm{v} \cdot \bm{v} = 1 / \left[p'(\alpha)\right]^2\), \(\bm{v} \cdot
\bm{w} = 0\) and \(\bm{w} \cdot \bm{w} = 1\). This produces
\begin{equation}
  \kappa_{\alpha, 0} = \sqrt{\frac{\mu_1^2 \left(\bm{v} \cdot \bm{v}\right) +
  0 + 0}{\alpha^2 + 0}} = \frac{\widetilde{p}(\alpha)}{\left|\alpha
  p'(\alpha)\right|},
\end{equation}
the commonly used condition number presented
in~\eqref{eq:bernstein-cond-num}.
